\documentclass[24pt,a4paper]{article}
\usepackage[left=12mm,top=0.5in,bottom=0.5in]{geometry}

\begin{document}
\title{A RESEARCH ON HOW TO PREPARE FOR MY NEXT SOCCER\ FOOTBALL MATCH. }
\maketitle

\section{Problem: }
The best way to prepare me and my teammates for the next soccer match.

\section{Scope: }
 the scope is briefly about how me as a captain interacts with couch to choose the team going to play as well as how they are going to play and put on.
\section{Interview:}
So I conduct an interview asking a few team supporters about which player plays best in different positions on the pitch. I do this to just get some assistance from people who have different aspects of different team players.
\section{Internet:}
I then continued my research to the internet where I looked comments on social media (twitter, facebook, whatsapp. etc) about the way we play as team or on how the different teammates play individually.\\
Making research about the opponents team and how they play (there style of football).\\Me and the couch get to know which players will face the opponents team best basing on their style of football. If you realize the attack a lot, then you make sure you  defend a lot, but if the defend a lot then it’s appropriate to play attacking football so that u can score some goals.\\
This is done just to ensure that you get some points out of the match.

\section{Materials required:}
The materials I need for research are , a recorder  to record the views of different people, I also need  a computer and internet access just for internet research and also access the social media platforms.
\section{Experimenting from research.}
In my research I needed to know which team would be best for different styles of football of different teams, so I interviewed very many people and also read a lot of comments from different social media platforms in order to come up with the best team that can help us win as a team.\\
I also arrange the team in different formations so that we can try out  different styles of play to find out which style suits us best.

\section{Challenges: }
As any other research, challenges were faced. These included;\\
Some people just give good comments about some players because they like them are related to them or just because they are good friends.\\
Some people give false comments about the team just because they don’t like the couch or the captain.
Some people give false comments just because they don’t like the style of play of the team.\\
Some people may give false comment just because they do not support the team and maybe supporters of the opponent team. 

\section{Theoretically:}
Theoretically I would prefer that we play an average style of football one that is not so defensive or attacking basically but both attacking and defensive in different aspects of the game.
\section{Conclusion.}
The more comments or views we get from different people who have interest in the team the more styles of football and formations we try out, this helps us to choose the best players in the team as well as the best playing style that will enable us win different games.
\section{KYAGERA SULAIMAN   15/U/6849/PS   215008420}
\end{document}